Run aquaculture model for Atlantic salmon

### 2025-08-04 06_run_atlantic_salmon_model.qmd
Chunk runs

targets::tar_load(stat_names)
targets::tar_load(farm_IDs_chunked) %>% unlist()
targets::tar_load(feed_names)

print("Loading farm results...")
targets::tar_load(farm_results_chunked)
for (stat_name in stat_names) {
  farm_results_chunked %>% 
      filter(measure == stat_name) %>% 
      qsave(file.path(output_model_farm_path, str_c(stat_name, "_all_farms.qs")))
}
rm(farm_results)

print("Loading cohort results...")
targets::tar_load(cohort_results)
for (stat_name in stat_names) {
  cohort_results %>% 
      filter(measure == stat_name) %>% 
      qsave(file.path(output_model_cohort_path, str_c(stat_name, "_all_farms.qs")))
}
rm(cohort_results)

targets::tar_load(biomass_produced)
qsave(biomass_produced, file.path(output_model_farm_path, str_c("biomass_produced_all_farms.qs")))
```

>>>>

targets::tar_load(stat_names)
targets::tar_load(farm_IDs_chunked)
farm_IDs_chunked <- farm_IDs_chunked %>% unlist()
targets::tar_load(feed_names)

print("Loading farm results...")
targets::tar_load(farm_results_chunked)
farm_results_chunked <- farm_results_chunked %>% 
  bind_rows()
for (stat_name in stat_names) {
  farm_results_chunked %>% 
      filter(measure == stat_name) %>% 
      qsave(file.path(output_model_farm_path, str_c(stat_name, "_all_farms.qs")))
}
rm(farm_results_chunked)

print("Loading cohort results...")
targets::tar_load(cohort_results_chunked)
cohort_results_chunked <- cohort_results_chunked %>% 
  bind_rows()
for (stat_name in stat_names) {
  cohort_results_chunked %>% 
      filter(measure == stat_name) %>% 
      qsave(file.path(output_model_cohort_path, str_c(stat_name, "_all_farms.qs")))
}
rm(cohort_results_chunked)

targets::tar_load(biomass_produced_chunked)
qsave(biomass_produced_chunked, file.path(output_model_farm_path, str_c("biomass_produced_all_farms.qs")))
rm(biomass_produced_chunked)
```
